Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-07-17 main.tex
Add further details about handshake mechanism.

@@

Interestingly none of these strategies are stochastic: this is explained by the
value of not provoking typically cooperative opponent strategies with
speculative defections. This includes opponents using the same strategy.  Acting
stochastically increases the chance of reducing the score of individuals of the
same type in a Moran process.  However it is possible to design a strategy with
a stochastic or error-correcting handshake that is an excellent resistor even in
noisy environments \cite{Lee2015}.

@@

\bibitem{Harper2017}
Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
  Glynatsi, and Owen Campbell.
\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
  Prisoner's Dilemma}.
\newblock arXiv:1707.06307, 2017.

@@

>>>>

The notion of a handshake has been described previously in~\cite{Robson1990} and
corresponds to idea that an individual exhibits behaviour that starts with a
recognisable pattern. This in turn allows them to identify memers of their own
type (who would exhibit the same pattern). This is analogous
to the biological notion of `kin recognition' where individuals have the ability
to recognise the phenotype of their own kin ~\cite{Mateo2003}.

@@

Interestingly none of these strategies are stochastic: this is explained by the
value of not provoking typically cooperative opponent strategies with
speculative defections. This includes opponents using the same strategy.  Acting
stochastically increases the chance of reducing the score of individuals of the
same type in a Moran process.  However it is possible to design a strategy with
a stochastic or error-correcting handshake that is an excellent resistor even in
noisy environments~\cite{Lee2015}.

@@

\bibitem{Harper2017}
Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
  Glynatsi, and Owen Campbell.
\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
  Prisoner's Dilemma}.
\newblock {\em PLOS ONE}, 12(12): 12 2017.

@@

\bibitem{Mateo2003}
Jill M. Mateo.
\newblock {Kin recognition in ground squirrels and other rodents}.
\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181
